---
title: "Rmarkdown Tutorial"
author: "Kate Wootton"
date: "April 1, 2019"
output: github_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

## Why Rmarkdown?

Rmarkdown lets you dynamically access data and generate figures, run analyses etc, making sure your research is reproducible. Cool things you can do

*	Show your code
*	Insert values from your data directly
*	Make figures
*	Tables
*	Reference sections / figures / equations (with bookdown)
*	Any language
*	Citations (bookdown)
* Version control (with git)


## What types of output? 

You can rapidly and easily change your output type to any of the following, and more:

*	Html
*	Word
*	Pdf (with Latex)
*	Github
*	Presentation (with beamer)
*	And more (e.g. tufte handout, Rshiny)


## How does it work?

### Sections

There are three main sections to the document:

*	Header
  *	What kind of document to create
  *	Title / author / date
*	Code chunks
  *	Surrounded by tick marks
  *	Indicate language
  *	Chunk options (e.g. warning = FALSE)
  *	Also inline
*	Text
  *	Formatting e.g. *bold*, **italics**, numbered lists, bullet points, headings
  *	Equations (using $  $ like latex)
  

## So let's do some stuff

### Figures

First we read in the data and make a plot. Note that our code is shown below so we know what we did and where the data came from (we can also suppress this if we want).

```{r favorite insect}
insects <- read.csv("../data/example_data.csv")
barplot(insects$frequency, names.arg = insects$insect)
```

### Referencing in text

Then we write about it:

It seems that `r insects[which(insects$insect == "flea beetle"), "frequency"]`people like flea beetles best.


### Equations

And here's an equation just for the sake of it: $e = mc^2$

### Tables

Maybe we want to see the data, so we can make a table:

```{r}
kable(insects, caption = "Table 1: Everyone's favourite insects")
```
